A generic and fast C++ optimization framework

### 2017-10-19 paper.tex
Add transition to Section 4.

{\bf <TODO: maybe we should add a table with optimizer types that work with
certain assumptions.  Maybe this can be a table, maybe a diagram, but some kind
of visual aid to split the space of objective function types would be nice.>}

>>>>

In some cases, some subclasses of functions can still be optimized with more
general optimizers.  For instance, separable objective functions can still be
optimized with an optimizer that does not specifically support separable
functions.  Similarly, a sparse differentiable function may be optimized with
any optimizer that can handle differentiable functions; however, that optimizer
may not take advantage of the sparseness.

Now, with an understanding of the types of functions that we wish to support and
their individual characteristics, we can develop an API that a given function
should implement the relevant parts of.
